---
title: "Biomedical Database Quality Report"
author: "Biomedical Data Management System"
date: "`r Sys.Date()`"
output: html_document

params:
  patients: NA
  audit_log: NA
  metrics: NA
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)

patients <- params$patients
audit_log <- params$audit_log
metrics <- params$metrics
```

# Executive Summary

This automated report summarizes the current state of the biomedical database, including patient statistics, data quality indicators, confidence scores, outlier detection, and audit activity.

---

# Database Overview

```{r echo=FALSE}
metrics$completeness_summary
```

---

# Clinical Indicators

## Average Patient Age

```{r echo=FALSE}
round(mean(patients$age, na.rm = TRUE), 1)
```

## Percentage of Smokers

```{r echo=FALSE}
round(mean(patients$smoker, na.rm = TRUE) * 100, 1)
```

---

# Sex Distribution

```{r echo=FALSE}
sex_data <- patients %>%
  count(sex)

ggplot(sex_data, aes(x = sex, y = n)) +
  geom_col(fill = "#1F4E79") +
  theme_minimal() +
  labs(
    title = "Sex Distribution",
    x = "Sex",
    y = "Number of Patients"
  )
```

---

# Blood Type Distribution

```{r echo=FALSE}
blood_data <- patients %>%
  count(blood_type)

ggplot(blood_data, aes(x = blood_type, y = n)) +
  geom_col(fill = "#2A9D8F") +
  theme_minimal() +
  labs(
    title = "Blood Type Distribution",
    x = "Blood Type",
    y = "Number of Patients"
  )
```

---

# Missing Values Analysis

```{r echo=FALSE}
metrics$missingness_by_variable
```

```{r echo=FALSE}
missing_plot_data <- metrics$missingness_by_variable %>%
  filter(missing_count > 0)

ggplot(missing_plot_data, aes(x = reorder(variable_name, missing_count), y = missing_count)) +
  geom_col(fill = "#5C6770") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Variables with Missing Values",
    x = "Variable",
    y = "Missing Values"
  )
```

---

# Record Confidence Score

```{r echo=FALSE}
metrics$record_confidence_score %>%
  arrange(confidence_score) %>%
  head(20)
```

---

# BMI Quality Table

```{r echo=FALSE}
metrics$bmi_table %>%
  head(20)
```

---

# Z-Score Outliers

```{r echo=FALSE}
metrics$zscore_outliers
```

---

# Recent Audit Activity

```{r echo=FALSE}
audit_log %>%
  arrange(desc(changed_at)) %>%
  select(
    table_name,
    record_id,
    action,
    changed_by,
    changed_at
  ) %>%
  head(20)
```

---

# Conclusions

The biomedical database demonstrates a functional architecture for clinical data ingestion, cleaning, storage, visualization, traceability, and automated reporting.

The implemented system supports:

- structured clinical records;
- secure patient insertion;
- validation before database insertion;
- storage of warning and critical quality flags;
- rejected-submission tracking;
- audit trail traceability;
- reactive dashboard visualization;
- missing-value analysis;
- BMI plausibility monitoring;
- z-score outlier detection;
- record-level confidence scoring;
- automated HTML reporting.

This workflow simulates a simplified biomedical information management system based on PostgreSQL, Shiny, validation rules, and data quality governance.